Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-02-22 paper/main.tex
Addressed referee suggestion number 3

Many sub-pulse drifters, e.g., B0809$+$74 and B0943$+$10, are known to have very stable drift rates \citep[e.g.][]{Taylor1971,Deshpande1999}.
This stability partly motivated the original carousel model, put forward by \citet{Ruderman1975}, which associates the sub-pulses with spatially discrete bursts of electrical discharges (``sparks'') in regions of charge depletion just above the stellar surface near the magnetic poles.
According to this model, the sparks are driven by \ExB{} drift, with the observed stability of the drift rate being directly inherited from the theoretical stability of the electric and magnetic fields at the spark locations.
Therefore, pulsars that exhibit anything more complicated than a single, stable drift rate deserve special attention, since they require modifications of, or at least extensions to, the basic carousel model.

Pulsars with complicated drifting behavior, and which are bright enough for single pulse analysis, are relatively rare.
Even a cursory glance at the drift bands of \psr{} show that its drifting behaviour is indeed complex, making it a welcome addition to this category of pulsar.
{\bf 
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to drifting behaviour, originally noticed by \citep{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, J1822$-$2256 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.
}

This paper presents an analysis of the nulling and drifting behaviour of \psr{} observed with the MWA.
Section \S\ref{sec:observations} describes the MWA observation in which the pulsar was originally found and the small number of archival MWA observations in which it was subsequently detected during follow up of the original candidate.
Analysis of the pulsar's nulling and drifting properties follows in Section \S\ref{sec:analysis}, which are discussed and compared to other pulsars in Section \S\ref{sec:discussion}.
We conclude with a short summary in Section \S\ref{sec:conclusions}.

@@

Its slow period and intermittent nature mean that long duration observations are required to collect a sufficiently large number of complete burst sequences to undertake robust statistical analysis on their properties.
Follow-up observations are currently under way at the uGMRT and at Murriyang, which will allow us to explore the drifting behaviour of \psr{} in much greater depth, as well as obtain a timing solution, refine the nulling fraction estimate, and perform a polarimetric analysis of its single pulses.

>>>>

Many sub-pulse drifters, e.g., B0809$+$74 and B0943$+$10, are known to have very stable drift rates \citep[e.g.][]{Taylor1971,Deshpande1999}.
This stability partly motivated the original carousel model, put forward by \citet{Ruderman1975}, which associates the sub-pulses with spatially discrete bursts of electrical discharges (``sparks'') in regions of charge depletion just above the stellar surface near the magnetic poles.
According to this model, the sparks are driven by \ExB{} drift, with the observed stability of the drift rate being directly inherited from the theoretical stability of the electric and magnetic fields at the spark locations.
Therefore, pulsars that exhibit anything more complicated than a single, stable drift rate deserve special attention, since they require modifications of, or at least extensions to, the basic carousel model.
{\bf
Such pulsars exist, and several extensions have been proposed over the years to account for them.
For example, \citet{Gil2000} suggest that a quasi-central spark can account for (non-drifting) core components in profiles, and the well-known phenomenon of bi-drifting may be explained by presence of an inner annular gap \citep{Qiao2004}, an inner acceleration gap \citep{Basu2020}, or non-circular spark motions \citep{Wright2017}.
Such extensions are typically developed to explain specific drifting behaviors that are observed in a relatively small subset of pulsars, and there still lacks a single, comprehensive theory that can describe all drifting behaviors.
}

{\bf
Pulsars that both show complicated drifting behavior and which are bright enough for single pulse analysis, are relatively rare.
}
Even a cursory glance at the drift bands of \psr{} show that its drifting behavior is indeed complex and bright, making it a welcome addition to this category of pulsar.
{\bf 
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to sub-pulse drifting, originally noticed by \citep{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, J1822$-$2256 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.
}

This paper presents an analysis of the nulling and drifting behavior of \psr{} observed with the MWA.
Section \S\ref{sec:observations} describes the MWA observation in which the pulsar was originally found and the small number of archival MWA observations in which it was subsequently detected during follow up of the original candidate.
Analysis of the pulsar's nulling and drifting properties follows in Section \S\ref{sec:analysis}, which are discussed and compared to other pulsars in Section \S\ref{sec:discussion}.
We conclude with a short summary in Section \S\ref{sec:conclusions}.

@@

Its slow period and intermittent nature mean that long duration observations are required to collect a sufficiently large number of complete burst sequences to undertake robust statistical analysis on their properties.
Follow-up observations are currently under way at the uGMRT and at Murriyang, which will allow us to explore the drifting behavior of \psr{} in much greater depth, as well as obtain a timing solution, refine the nulling fraction estimate, and perform a polarimetric analysis of its single pulses.
